|

### 2023-02-09 paper.Rmd
autogit

...

@@

The aim of Estimation of distribution algorithms (EDA) is to replace the standard variation operators used in GA by building probabilistic models that can capture complex dependencies between different decision variables of an optimization problem [@design_of_modern_heuristics].
EDAs use this probabilistic model to sample new offspring solutions inside an evolutionary search to replace crossover and/or mutation operators.
Even though a majority of EDA algorithms are designed to work with fixed length string representations as used in classical GAs, EDA algorithms have been researched an successfully applied to the domain of GP in various different research streams.

@@

...describe different pre-training strategies, e.g. few shot, perpetual, re-using...

-- describe unsupervised vs supervised pre-training...

>>>>

Denoising Autoencoder Genetic Programming (DAE-GP) is an Estimation of Distribution Algorithm in the domain of Genetic Programming that uses Denoising Autoencoders Long Short-Term Memory Networks (DAE-LSTM) as probabilistic models for sampling new populations of solutions.
This thesis investigates the possible benefits and downsides of using pre-training for the DAE-LSTM networks of DAE-GP for four real world symbolic regression problems.
The Experiments conducted did show that pre-training can drastically reduce the number of training epochs that are necessary at each generation of the DAE-GP search while also increasing the diversity of the population.
Unfortunately pre-training did not show any improvements for both final fitness and the final size of solutions while largley increasing the total run-time for DAE-GP.

# Keywords {.unlisted .unnumbered}

Genetic Programming, Estimation of Distribution Algorithms, Denoising Autoencoder Genetic Programming, Pre-Training, Long Short-Term Memory Networks, Symbolic Regression

@@

The aim of Estimation of distribution algorithms (EDA) is to replace the standard variation operators used in GA by building probabilistic models that can capture complex dependencies between different decision variables of an optimization problem [@design_of_modern_heuristics].
EDAs use this probabilistic model to sample new offspring solutions inside an evolutionary search to replace crossover and/or mutation operators.
Even though a majority of EDA algorithms are designed to work with fixed length string representations as used in classical GAs, EDA algorithms have been researched an successfully applied to the domain of GP in various different research streams [@kim_probMod_GP].

@@
